\Large{Adversarial Variational Optimization of Non-Differentiable Simulators}

### 2017-06-14 paper.tex
GAN section

Given some observed data $\{ \mathbf{x}_i | i=1, \dots, N \}$ drawn from the (unknown) true distribution $p_r$, our goal is the inference
of the parameters of interest $\mathbf{\theta}^*$ that minimize the divergence
between $p_r$ and the modeled
data distribution $p_\mathbf{\theta}$ induced by $g(\cdot; \mathbf{\theta})$. That is,
\begin{equation}
    \mathbf{\theta}^* = \arg \min_\mathbf{\theta} \rho(p_r, p_\mathbf{\theta}),
\end{equation}
where $\rho$ is some distance or divergence.

@@

Generative adversarial networks (GAN) were first proposed by
\cite{goodfellow2014generative} as a way to build an implicit generative model
capable of producing samples from random noise $\mathbf{z}$. More specifically,
a generative model $g(\cdot; \mathbf{\theta})$ is pit against an adversarial
network $d$ whose antigonistic objective is to recognize real data $\mathbf{x}$
from generated data $g(\mathbf{z}; \mathbf{\theta})$. Both models $g$ and $d$
are trained simultaneously, in such a way that $g$ learns to maximally confuse
its adversary $d$ (which happens when $g$ produces samples comparable to the
observed data), while $d$ continuously adapts to changes in $g$. When $d$ is
trained to optimality before each parameter update of the generator, it can
be shown that the original adversarial learning procedure amounts to minimizing
the Jensen-Shannon divergence between $p_r$ and $p_\theta$.

More recently, ...

\glnote{Explain WGAN, loss and optimum.}

>>>>

Given some observed data $\{ \mathbf{x}_i | i=1, \dots, N \}$ drawn from the (unknown) true distribution $p_r$, our goal is the inference
of the parameters of interest $\mathbf{\theta}^*$ that minimize the divergence
between $p_r$ and the modeled
data distribution $p_\mathbf{\theta}$ induced by $g(\cdot; \mathbf{\theta})$ over $\mathbf{z}$. That is,
\begin{equation}
    \mathbf{\theta}^* = \arg \min_\mathbf{\theta} \rho(p_r, p_\mathbf{\theta}),
\end{equation}
where $\rho$ is some distance or divergence.

@@

Generative adversarial networks (GANs) were first proposed by
\cite{goodfellow2014generative} as a way to build an implicit generative model
capable of producing samples from random noise $\mathbf{z}$. More specifically,
a generative model $g(\cdot; \mathbf{\theta})$ is pit against an adversarial
classifier $d(\cdot; \phi):\mathbb{R}^d \to [0,1]$ whose antagonistic objective is to recognize real data $\mathbf{x}$
from generated data $g(\mathbf{z}; \mathbf{\theta})$. Both models $g$ and $d$
are trained simultaneously, in such a way that $g$ learns to maximally confuse
its adversary $d$ (which happens when $g$ produces samples comparable to the
observed data), while $d$ continuously adapts to changes in $g$. When $d$ is
trained to optimality before each parameter update of the generator, it can
be shown that the original adversarial learning procedure amounts to minimizing
the Jensen-Shannon divergence $\text{JSD}(p_r \parallel p_\theta)$ between $p_r$ and $p_\theta$.

As thoroughly explored in \citep{2017arXiv170104862A}, GANs remain remarkably
difficult to train because of vanishing gradients as $d$ saturates, or because of
unreliable updates when the training procedure is relaxed. As a remedy,
Wasserstein GANs~\citep{2017arXiv170107875A} reformulate the adversarial
setup in order to minimize the Wasserstein-1 distance $W(p_r, p_\theta)$ by
replacing the adversarial classifier with a 1-Lipschitz adversarial critic
$d(\cdot; \phi) : \mathbb{R}^d \to \mathbb{R}$. Under the WGAN-GP formulation of \cite{2017arXiv170400028G},
training $d$ and $g$ results in alternating gradient updates on $\phi$ and $\theta$ in order to respectively minimize
\begin{align}
    {\cal L}_d =\,& \mathbb{E}_{\tilde{\mathbf{x}} \sim p_\theta} [d(\tilde{\mathbf{x}};\phi)] - \mathbb{E}_{\mathbf{x} \sim p_r} [d(\mathbf{x};\phi)]  \nonumber \\
                  & + \lambda \mathbb{E}_{\hat{\mathbf{x}} \sim p_{\hat{\mathbf{x}}}} [(|| \nabla_{\hat{\mathbf{x}}} d({\hat{\mathbf{x}}};\phi) ||_2 - 1)^2] \\
    {\cal L}_g =\,& -\mathbb{E}_{\tilde{\mathbf{x}} \sim p_\theta} [d(\tilde{\mathbf{x}};\phi)]
\end{align}
where ${\hat{\mathbf{x}}} := \epsilon \mathbf{x} + (1-\epsilon)\tilde{\mathbf{x}}$, for $\epsilon \sim U[0,1]$, $\mathbf{x} \sim p_r$ and $\tilde{\mathbf{x}} \sim p_\theta$.
